On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-23 4_Result.tex

\begin{table*}[htbp]
\caption{Time in seconds to submit a correct answer}
\label{tab:difference-time-taken}
\centering{
\begin{tabular}{lccc|cc} \toprule
Atom & Confusing Code & Clean Code & $\Delta$(\%) & Mann-Whitney test & Cliff's Delta \\ \midrule 
Comma Operator & 87.67 & 20.84 & -76.23 &  \colorbox{lightgray}{$<$ 0.01} & -0.53 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 &  \colorbox{lightgray}{$<$ 0.01} & -0.39 \\ 
% {\color{red}Automatic Semicolon Insertion} & 46.08 & 22.04 & -52.17 & 0.09 & -0.16 \\ 
Omitted Curly Braces & 48.85 & 30.00 & -38.58 & 0.92 & -0.01 \\ 
Implicit Predicate & 36.24 & 24.01 & -33.75 & \colorbox{lightgray}{$<$ 0.01} & -0.29 \\ 
Post Increment & 28.70 & 25.67 & -10.56 & 0.12 & 0.15 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 & 0.82 & 0.02 \\ 
Ternary Operator & 41.80 & 39.34 & -5.90 & 0.24 & -0.12 \\ 
Arithmetic as Logic & 28.82 & 37.20 & +29.06 & \colorbox{lightgray}{0.01} & 0.23 \\ 
Pre-Increment & 30.71 & 42.45 & +38.19 & \colorbox{lightgray}{$<$ 0.01} & 0.27 \\ 
         \bottomrule
    \end{tabular}}
\end{table*}

>>>>

% \begin{table*}[htbp]
% \caption{Time in seconds to submit a correct answer}
% \label{tab:difference-time-taken}
% \centering{
% \begin{tabular}{lccc|cc} \toprule
% Atom & Confusing Code & Clean Code & $\Delta$(\%) & Mann-Whitney test & Cliff's Delta \\ \midrule 
% Comma Operator & 87.67 & 20.84 & -76.23 &  \colorbox{lightgray}{$<$ 0.01} & -0.53 \\ 
% Logic as Control Flow & 108.94 & 51.07 & -53.12 &  \colorbox{lightgray}{$<$ 0.01} & -0.39 \\ 
% % {\color{red}Automatic Semicolon Insertion} & 46.08 & 22.04 & -52.17 & 0.09 & -0.16 \\ 
% Omitted Curly Braces & 48.85 & 30.00 & -38.58 & 0.92 & -0.01 \\ 
% Implicit Predicate & 36.24 & 24.01 & -33.75 & \colorbox{lightgray}{$<$ 0.01} & -0.29 \\ 
% Post Increment & 28.70 & 25.67 & -10.56 & 0.12 & 0.15 \\ 
% Assignment as Value & 52.47 & 48.95 & -6.71 & 0.82 & 0.02 \\ 
% Ternary Operator & 41.80 & 39.34 & -5.90 & 0.24 & -0.12 \\ 
% Arithmetic as Logic & 28.82 & 37.20 & +29.06 & \colorbox{lightgray}{0.01} & 0.23 \\ 
% Pre-Increment & 30.71 & 42.45 & +38.19 & \colorbox{lightgray}{$<$ 0.01} & 0.27 \\ 
%          \bottomrule
%     \end{tabular}}
% \end{table*}

 % latex table generated in R 4.0.4 by xtable 1.8-4 package
 % Thu Apr 22 07:58:21 2021
 \begin{table*}[ht]
\caption{Time in seconds to submit a correct answer}
\label{tab:difference-time-taken}

 \centering
 \begin{tabular}{rllrlrrlr}
   \hline
  & Atom & ChiTest & Odds Ratio Correctness & p-value & CI 2.5\% & CI 97.5\% & Wilcox Test (Time) & Cliff Delta \\ 
   \hline
 3 & Automatic Semicolon Insertion & 5.8352e-11 & 39.33 & 2.4351e-12 & 9.21 & 356.62 & 0.09802 & -0.16 \\ 
   4 & Comma Operator & 1.1727e-10 & 19.02 & 1.5812e-11 & 6.60 & 68.22 & 5.8249e-08 & -0.53 \\ 
   2 & Assignment as Value & 0.0034775 & 8.39 & 0.0024331 & 1.81 & 79.12 & 0.82681 & 0.02 \\ 
   6 & Implict Predicate & 0.01123 & 6.95 & 0.008974 & 1.46 & 66.56 & 0.0029039 & -0.29 \\ 
   9 & Post Increment & 0.0015279 & 4.83 & 0.0012328 & 1.73 & 15.74 & 0.12006 & 0.15 \\ 
   5 & Ternary Operator & 0.15896 & 2.73 & 0.15712 & 0.74 & 12.57 & 0.24073 & -0.12 \\ 
   8 & Ommitted Curly Braces & 0.050962 & 2.35 & 0.050056 & 1.00 & 5.77 & 0.92529 & -0.01 \\ 
   7 & Logic as Control Flow & 0.292 & 1.54 & 0.29198 & 0.73 & 3.28 & 7.5862e-05 & -0.39 \\ 
   10 & Pre Increment & 0.70147 & 1.25 & 0.70181 & 0.55 & 2.85 & 0.0062981 & 0.27 \\ 
   1 & Arithmetic as Logic & 1 & 0.84 & 1 & 0.22 & 3.12 & 0.01723 & 0.23 \\ 
    \hline
 \end{tabular}
 \end{table*}
